---
output:
  beamer_presentation:
    fig_crop: FALSE
    toc: true
    slide_level: 2
---

```{r setup, include=FALSE}
source("main.R", local = knitr::knit_global())
library(knitr)
opts_chunk$set(echo = FALSE, fig.width = 15, fig.height = 12)
library(xtable)
bold <- function(x) {paste('{\\textbf{',x,'}}', sep ='')}
```

---
title: "`r format(LAST_DATE, '%B %Y')`"
---

# Rates

```{r, echo=F, results = "asis", message=FALSE, warning=FALSE}
for(currency in currencies[currencies!='UAH']){
   cat("\n\n##", currency, "/ UAH Rate \n")
   print(uahRatePlot(uah_rates, currency))
}
```

# Flows
```{r, echo=F}
flowsTotalsPlot(uah_flw)
```

## Margin
```{r, echo=F}
marginDynamicsPlot(uah_flw)
```

## Flows Dynamics
```{r, echo=F, warning=FALSE}
flowsAbsPlot(uah_flw)
```

## Flows share

```{r, echo=F}
flowsTotalShares(shareDf)
```

## Expenses share

```{r, echo=F, warning=FALSE}
flowsTypeShare(shareDf, T)
```

## Expenses Distribution
```{r, echo=F, warning=FALSE}
flowsDistributionPlot(uah_flw, T)
```

## Expenses Dynamics

```{r, echo=F, warning=FALSE}
expencesDynamicsPlot()
```

## Income share

```{r, echo=F, warning=FALSE}
flowsTypeShare(shareDf)
```

## Income Distribution
```{r, echo=F, warning=FALSE}
flowsDistributionPlot(uah_flw, F)
```

## Income Dynamics

```{r, echo=F, warning=FALSE}
incomeDynamicsPlot()
```

```{r, echo=F, results = "asis", message=FALSE, warning=FALSE}
for (column in FLOWS) {
  cat("\n\n##", column, " dynamics \n")
  print(flowAbsDynamicsPlot(flows_dat, column))
  cat("\n\n##", column, " share\n")
  print(flowRelDynamicsPlot(uah_flw, column))
}
```

# Holdings

## Dynamics by currency 
```{r, echo=F, warning=FALSE}
currencyDynamicsPlot(hold_total)
```

## Currency
:::::: {.columns}
::: {.column width="60%"}
```{r, echo=FALSE, results='asis'}
print(xtable(hold_total[, currencies]), scalebox='0.5', comment=FALSE, sanitize.colnames.function=bold, sanitize.rownames.function=bold)
```
:::

::: {.column width="60%"}
```{r, echo=F, warning=FALSE}
currencySharePlot()
```
:::
::::::

## Currency consolidation

```{r, echo=FALSE, results='asis'}
xt <- xtable(hold_total[, c('abs', paste0('uah_', currencies))])
names(xt) <- c("Total", currencies)
print(xt, scalebox='0.5', comment=FALSE, sanitize.colnames.function=bold, sanitize.rownames.function=bold)
```

## Portfolio by currency 
```{r, echo=F, warning=FALSE}
currencyPortfolioPlot(hold_total)
```

```{r, echo=F, results = "asis", message=FALSE, warning=FALSE}
for(currency in currencies){
   if(sum(tail(hold_total[,currency], n=3))>0){
      
      cat("\n\n##", currency, " dynamics \n")
      print(currencyHoldingsPlot(hold_total, currency, "currencyDynamics"))
      
      cat("\n\n##", currency, " growth \n")
      print(currencyHoldingsPlot(hold_total, currency, "currencyDiffAbs"))
      
      cat("\n\n##", currency, " performance \n")
      print(currencyHoldingsPlot(hold_total, currency, "currencyDiffRel"))
      
      cat("\n\n##", currency, " by place performance \n")
      print(placeChangePlot(currency))
      
      jpeg(paste0('plots/',currency,'_placeSharePlot.jpg'), width = 520, height = 548)
      print(placeSharePlot(currency))
      dev.off()
      
      cat("\n\n##", currency, " share by place\n")
      
      cat("\\begin{columns}")
      cat("\\begin{column}{0.6\\textwidth}")
      print(xtable(getPlaceHistoryTable(currency)), scalebox='0.4', comment=FALSE, sanitize.colnames.function=bold, sanitize.rownames.function=bold)
      cat("\\end{column}")
      cat("\\begin{column}{0.4\\textwidth}")
      cat("\\vspace*{-6cm}")
      cat("\\hspace*{-0.5cm}")
      cat("\\includegraphics[scale=.3]{",paste0('plots/',currency,'_placeSharePlot.jpg'),"}",sep = "")
      cat("\\end{column}")
      cat("\\end{columns}")
   }
}
```

## Place diversification

:::::: {.columns}
::: {.column width="50%"}
```{r, echo=FALSE, results='asis'}
print(xtable(diversificationTable(placeConsolidation, pretty=T)), scalebox='0.5', comment=FALSE, sanitize.colnames.function=bold, sanitize.rownames.function=bold)
```
:::
::: {.column width="80%"}
```{r, echo=FALSE, results='asis'}
diversificationPiePlot(t(tail(placeConsolidation, n=1)), palette=placesScale)
```
:::
::::::

## Place performance
```{r, echo=FALSE, results='asis'}
diversificationPerformancePlot(diversificationTable(placeConsolidation))
```

## Place consolidation
```{r, echo=FALSE, results='asis'}
diversificationBarPlot(t(tail(placeConsolidation, n=1)), palette=placesScale)
```

## Dynamics by Holding Type 
```{r, echo=F, warning=FALSE}
holdingTypesDynamicsPlot(hold_total)
```

## UAH Dynamics by Holding Type
```{r, echo = FALSE, results = 'asis'}
print(xtable(hold_total[, holdingTypes] %>% select_if(function(col) !!(sum(tail(col, n=6))) )), scalebox='0.4', comment=FALSE, sanitize.colnames.function=bold, sanitize.rownames.function=bold)
```

## Portfolio by Holding Type 
```{r, echo=F, warning=FALSE}
holdingTypesPortfolioPlot(hold_total)
```

```{r, echo=F, results = "asis", message=FALSE, warning=FALSE}
for(holding in HOLDINGS){
   cat("\n\n##", holding, " dynamics \n")
   print(holdAbsDynamicsPlot(holdings,hold_meta,hold_uah, holding))
}
```

# Investments

```{r, echo=F, results = "asis", message=FALSE, warning=FALSE}
for(investmentType in rownames(investments)){
   cat("\n\n##", investmentType, " Yield \n")
  print(investmentsYieldPlot(investmentType))
}
```

# Errors

## Profit calculations
```{r, echo=F, warning=FALSE}
profitsPlot(hold_total)
```

## Profit by currency
```{r, echo=F, warning=FALSE}
currencyErrors()
```

## Error absolute
```{r, echo=F, warning=FALSE}
profitErrorAbs(hold_total)
```

## Error relative
```{r, echo=F, warning=FALSE}
profitErrorRel(hold_total)
```

# Appendix

```{r, echo=F, results = "asis", message=FALSE, warning=FALSE}
for(year in STORED_YEARS){
   cat("\n\n##", year, " Holdings\n")
   print(xtable(appendixHoldingsYearTable(year)), scalebox='0.35', comment=FALSE, sanitize.colnames.function=bold, sanitize.rownames.function=bold)
   cat("\n\n##", year, " Flows\n")
   print(xtable(appendixFlowsYearTable(year)), scalebox='0.4', comment=FALSE, sanitize.colnames.function=bold, sanitize.rownames.function=bold)
}
```